\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-24 draft/paper.tex
2.2 The pseudo-Cl method: fixed typo

      Before we move on to covariances, it is worth considering the case of unmasked field (i.e $w^a({\bf x})=1$ everywhere). In this case $\,^a{\sf M}_{{\bf l}{\bf l}'}=\mathds{1}\Delta^x({\bf k},{\bf l})$, and therefore different modes are uncorrelated (as should have been obvious). In a non-ideal case where the mask is still sufficiently well behaved (i.e. masks without too much small-scale structure), we can still expect the coupling coefficients $\,^a{\sf M}_{{\bf l}{\bf l}'}$ to be sharply peaked around ${\bf l}={\bf l}'$.

>>>>

      Before we move on to covariances, it is worth considering the case of
      unmasked field (i.e $w^a({\bf x})=1$ everywhere). In this case $\,^a{\sf
        M}_{{\bf l}{\bf l}'}=\mathds{1}\Delta^x({\bf l},{\bf l}')$, and therefore different modes are uncorrelated (as should have been obvious). In a non-ideal case where the mask is still sufficiently well behaved (i.e. masks without too much small-scale structure), we can still expect the coupling coefficients $\,^a{\sf M}_{{\bf l}{\bf l}'}$ to be sharply peaked around ${\bf l}={\bf l}'$.
